Holomorphic field theories and higher algebra

### 2024-09-18 draft.tex
i guess i did not save and push at office last night

We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
There is a another class of holomorphic gauge theories 
defined on any complex manifold, with no restriction on dimension 
and without the need for a Calabi--Yau structure.

Let $X$ be a complex manifold of complex dimension~$n$.
Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra~$\fg$.
Fix a holomorphic principal $G$-bundle $P \to X$.
The fields consist of pairs $(A,B)$ where 
\[
A \in \Omega^{0,1}(X, \fg_P)
\] 
where $\fg_P$ is the adjoint bundle of $P$ and
\beqn
B \in \Omega^{n,n-2}(X, \fg_P^*) ,
\eeqn
where $\fg_P^*$ is the coadjoint bundle of $P$. 
The action functional is 
\beqn
S(A,B) = \int_X \langle B \wedge F_A \rangle
\eeqn
where $F_A$ is the curvature of the connection $A$.
The equations of motion are
\[
F_A^{0,2} = \dbar A + \frac12 [A,A] = 0 \text{ and } \dbar B + [A,B] = 0.
\]
A solution to the first equation provides is a $\dbar$-connection 
\[
\dbar_A = \dbar_P + [A,-]
\]
on the underlying smooth bundle $P\to X$, 
\owen{Am I doing that right? I believe a choice of holomorphic structure on $P$ automatically determines a Dolbeault operator, or $\dbar$-connection.}
and a solution to the second equation is a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle associated to~$\dbar_A$.
This theory is often called {\em holomorphic BF theory}, due to the integrand of the action functional.

\begin{rmk}
Notice that this action functional resembles the $\beta\gamma$ system, 
with $A$ playing the role of $\gamma$ and $B$ playing the role of $\beta$.
A physicist might also recognize this action functional as a holomorphic analog of topological $BF$ theory. 
\end{rmk}

It is natural to view two connections as equivalent if they are related by a gauge transformation
and to identify $B$-solutions that are related by a $\dbar_A$-exact term.
From the point of view of derived geometry,
we thus see holomorphic BF theory as describing the moduli space
\[
T^*[-1] \Bun_G(X),
\]
if we run over all principal bundles.

\begin{rmk}
Holomorphic BF theory exhibits some interesting properties at the quantum level,
at least perturbatively.
For example, in \cite{semichiral} it is shown that on $X = \C^2$ 
the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
More precisely, to first-order in perturbation theory, 
the stress tensor has a divergence-free component that is cohomologically trivial. 
In other words, the quantum theory appears to be ``invariant'' under divergence-free vector fields,
although not all vector fields (as in the case of a TFT).
\owen{Add specific location in text.}
\end{rmk}

@@

\begin{thm}[Wang, \owen{precise citations}]
For every graph~$\gamma$,
this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
That is, there is a smooth map
\[
w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
\]
where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.
\end{thm}

>>>>

We have already met holomorphic Chern--Simons theory, which is defined on Calabi--Yau three-folds.
There is a related holomorphic gauge theory that is defined in arbitrary complex dimensions and does not require the data of a Calabi--Yau structure. 
Fix a complex Lie group $G$ and an invariant symmetric bilinear form $\langle-,-\rangle$ on its Lie algebra.

If $n$ is the complex dimension of $X$, 
the fields consist of pairs $(A,B)$ where $A$ denotes a $\dbar$-connection on a holomorphic principal $G$-bundle $P \to X$ and
\beqn
B \in \Omega^{n,n-2}(X, \fg_P^*) ,
\eeqn
where $\fg_P$ is the adjoint bundle of $P$. 
The action functional is 
\beqn
S(A,B) = \int_X \langle B \wedge F_A \rangle
\eeqn
where $F_A$ is the curvature of the connection $A$.
From this formula, one might see that the model is a holomorphic analog of topological $BF$ theory. 
Notice that locally on $X$ and
writing the connection at $\dbar + [A,-]$, this action can be written as
\beqn
S(A,B) = \int_X \langle B \wedge \left(\dbar A + \frac12 [A,A]  \right) \rangle.
\eeqn
The equations of motion are
\[
F_A^{0,2} = \dbar A + \frac12 [A,A] = 0 \text{ and } \dbar B + [A,B] = 0.
\]
In other words, a solution is a $\dbar$-connection on $P\to X$ and a holomorphic $(n,n-2)$-form-valued section of the coadjoint bundle.

Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is a almost topological field theory.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory. \owen{Add specific location in text.}}

@@

\begin{thm}[Wang, \owen{precise citations}]
For every graph~$\gamma$,
this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
That is, there is a smooth map
\[
w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
\]
where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
\end{thm}
